---
title: "Do Bigger Hospitals provide better or worse care?"
author: "Jonathan Katz"
date: "January 9, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/IntroDS/IntroDS_Pierrepont/Rprog/hospital readmit outcome/")
outcome <- read.csv("outcome-of-care-measures.csv", colClasses = "character")
readmit <- read.csv("Hospital_Readmissions_Reduction_Program.csv", colClasses = "character")
```

## R Markdown

Hypothethis:

Larger hospitals give overall better care.

(as.double(f[, 11])/(0.01*f[, 15]))

Analysis:

To analyze the data, I will first finding the total number of patients who are hospitalized for a certain condition per 30 days, which I will find by dividing the Hospital 30 day death rate by the Hospital's mortality rate x 0.01.

Then I will graph a scatterplot of the total number of patients hospitalized for a condition vs. the mortality rate.

```{r warning=FALSE}
cleaned_data = sapply(outcome, as.numeric)

condition_rate_i = 11

num_of_patients_i = 15

condition_rate = cleaned_data[, condition_rate_i]
total = (cleaned_data[, num_of_patients_i]/(cleaned_data[, condition_rate_i]*0.01))
plot(total, condition_rate, xlab = "Patients admitted for condition", ylab = "Mortality rate for condition", type = "p")
hist(condition_rate, breaks=40, col="red")
```